Type-Safe Modular Parsing

### 2016-12-19 paper/sections/Introduction.tex
contributions

\item {\name:} A parser combinator library that allows the development 
of modular parser.

>>>>

\item {\name:} A parser combinator library that allows the development 
of modular parser. The library uses \emph{delegation} and
\emph{Object-Algebras} to achieve modularity and extensibility.

\item {{\bf A Parsing Technique for OO ASTs:}} A simplified version of
  our technique also enables parsing OO-style ASTs, where new language
  constructs can be easily added.

\item {{\bf Limitations of existing Parser Combinator Techniques:}}
\bruno{Improve and write something here.}
